\documentclass{martinwimmers_cv}

\setname{Martin}{Wimmers}
\setaddress{Nijmegen/Netherlands}
\setmail{martinwimmers@gmail.com}
\setlinkedinaccount{https://nl.linkedin.com/in/martin-wimmers-8aaba6145} %you can play with color of the template (red is also nice..)
\setgithubaccount{https://github.com/sirmrmarty} %you can play with color of the template (red is also nice..)
\setthemecolor{black} %you can play with color of the template (red is also nice..)

\begin{document}
%Set variables
%You can add sections, texts, explanations just by copying the style below. Replace the dummy texts "\lipsum[1][x-x]\par" with actual texts.
%Create header
\headerview
\vspace{1ex}
%Sections
%
% Summary
\addblocktext{Summary}{I am currently pursuing an MSc in Neuroscience, where my research focuses on stimulating the thalamus using transcranial ultrasound. My passion for neuroscience stems from its unique combination of two fields I am deeply interested in: Engineering and Psychology. I thrive in environments where I can create and innovate, and I am always eager to take on challenges, whether working independently or collaborating within a team. I’m comfortable diving into new situations with minimal supervision and excel at bringing ideas to life through a hands-on approach.}
%
%Education
\section{Education} 
    \datedexperience{Berufskolleg Wesel}{2015-2018} 
    \explanation{A-Levels Engineering Science} 
     \explanationdetail{Consisting of Constructional Engineering, Mechanical Engineering, Electrical Engineering, Math and Physics
     }
    \datedexperience{Radboud University}{2018-2022} 
    \explanation{BSc in Psychology} 
     \explanationdetail{How Perceived Discrimination Effects Negative Linguistic, Intergroup Bias, in a Dutch Minority Sample \\
     \explanationdetailsmall{Supervisor: Dr. Gijs Bijlstra}}
    \datedexperience{Radboud University, Donders Institute for Cognition}{2022-Present} 
    \explanation{MSc Cognitive Neuroscience} 
    \explanationdetail{Towards Robust Neuromodulation of the thalamus: Biasing Decision Flexibility with Thalamic Ultrasound Stimulation. \\
    \explanationdetailsmall{VerhagenLab for Cognitive Neuromodulation, PI: Dr. Lennart Verhagen, Supervisior: Dr. Julian Kosciessa}
     }
\vspace{-.3cm}
% Experience
\section{Resarch Experience}
    %
    \datedexperience{Donders Institute - Center for Cognition}{02.2022-03.2022, Nijmegen} 
    \explanation{Research Assistant} 
    \explanationdetailsmall{Assisting EEG, EMG and Robot research project of Yvonne Visser on corticomascular coherence at the Donders Center for Cognition by acquired data of more than 10 pilot subjects.}
    %
    \datedexperience{Radboud University Medical Center, Radboud University}{2023-2024 / Nijmegen} 
    \explanation{Student Assistant, 2023 / 2024}
    \explanationdetailsmall{VR development for education. Supervisor: Dr. Nils Kohn DCCN}
    \explanation{Teaching Assistant, 2023 / 2024}
    \explanationdetailsmall{Course Neuroanatomy. Dissection of human and rad brains. Supervisor: Dr. Marijtje Jongsma DCMN}
    \explanation{Teaching Assistant, 02.2024-07.2024} 
    \explanationdetailsmall{Workgroup teacher for Research Project 2 part of BSc Psychology}
    \explanation{Research Assistant, 10.2023-08.2024}
    \explanationdetailsmall{Cognitive Neuromodulation Lab at Donders Center for Cognition. TUS demonstration and education. Dr. Lennart Verhagen}
    %
    \datedexperience{Radboud University, Donders Institute for Cognition}{2023-Now / Nijmegen} 
    \explanation{Master Internship} 
    \explanationdetailsmall{
     Research Intern at the Cognitive Neuromodulation Lab of Dr. Lennart Verhagen under the supervision of Dr. Julian Kosciessa. Holistic involvement in conducting a MR/EEG/TUS study.}
\vspace{-0.2cm}
% Skills
\section{Skills}
    %
    \newcommand{\skillone}{\createskill{Programming Languages}{\textbf{\emph{Experienced:}} \ \  Python \cpshalf MatLab \cpshalf R\ \ \textbf{\emph{Familiar:}} \ \  Node.JS  \cpshalf Bash }}
    %
    \newcommand{\skilltwo}{\createskill{Neuroimaging Techniques}{EEG acquisition and processing (certified user) \cpshalf MR acquisition and processing}}
    %
    \newcommand{\skillthree}{\createskill{NIBS Techniques}{Transcranial Ultrasound Stimulation (certified user)}}
    \newcommand{\skillfour}{\createskill{Frameworks \ \& \ Libraries}{Bidscoin \cpshalf PsychoPy \cpshalf PsychToolBoxv \cpshalf PRESTUS \cpshalf K-Wave}}
    %
    \newcommand{\skillfive}{\createskill{Languages}{\textbf{\emph{Native:}} \ \  German \ \ \textbf{\emph{Fluent:}} \ \ English \ \ \textbf{\emph{Beginner:}} \ \  Dutch }}
    %
    \createskills{\skillone, \skilltwo, \skillthree, \skillfour, \skillfive}
\vspace{-0.5cm}
% Experience
\section{Extra}
    \newcommand{\extraone}{\textbf{Front and Backend Developer at NewHanagar:} Lead the development of robust full-stack solutions, implementing efficient front-end interfaces and scalable back-end architectures to support diverse user needs.}
    %
    \newcommand{\extratwo}{\textbf{Event Management Experience:} Successfully served as the head organizer for more than three major events, overseeing all aspects of planning, administration, and execution to ensure seamless operations and impactful experiences.}
    %
    \newcommand{\extrathree}{\textbf{G.Tec Spring Summer School (2023 \& 2024):} Participated in intensive courses focused on cutting-edge technologies, further enhancing my skills in advanced tech solutions and innovation.}
    %
    \newcommand{\listofextras}{\extraone, \extratwo, \extrathree}
    %
    \createbullets{\listofextras}
%Footnote
\vspace{-0.5cm}
\createfootnote
\end{document}
